Models

### 2023-10-02 analysis/dag.qmd
ggdag updates

library(tidyverse)
library(dagitty)
library(ggdag)
library(here)

@@

```{r dag}
#| fig-width: 10

dag_laterality <- dagify(ich_laterality ~ functional_outcome)

dag_laterality |>
  ggdag()

@@

>>>>

library(tidyverse)
library(dagitty)
library(ggdag)
library(MetBrewer)
library(here)
library(broom) # For converting model output to data frames

# set theme of all DAGs to `theme_dag()`
theme_set(theme_dag(base_family = "Cantarell"))

@@

```{r dag, warning=FALSE, message=FALSE}
#| fig-width: 10
#| fig-height: 7

# original DAG: dagitty.net/mcLgZ8X, pw: CDKM93kbXs

node_details <- tribble(
  ~name, ~label, ~x, ~y,
  "functional_disability", "Functional Disability", 4, 1,
  "ich_laterality", "Hemispheric Laterality", 1, 1,
  "age", "Age", 2.75, 3,
  "ich_location", "ICH Location", 2, 2.75,
  "ich_volume", "ICH Volume", 1, 2.75,
  "ivh", "IVH", 1.5, 2.25,
  "gcs_baseline", "Admission GCS", 2, 3.25,
  "wlst", "Early WLST", 3.75, 2.25,
  "neurosurgery", "Neurosurgery", 2, 1.5,
)

node_labels <- node_details$label
names(node_labels) <- node_details$name

ich_dag <- dagify(
  functional_disability ~ ich_laterality + age + ich_location + ich_volume + ivh + gcs_baseline + wlst + neurosurgery,
  neurosurgery ~ ich_laterality + age + ich_location + gcs_baseline,
  wlst ~ age + ich_location + gcs_baseline + ich_volume + ivh,
  gcs_baseline ~ age + ich_location + ich_volume + ivh,
  ich_location ~ age,
  ivh ~ ich_location,
  exposure = "ich_laterality",
  outcome = "functional_disability",
  coords = node_details,
  labels = node_labels
)

ich_dag_tidy <- ich_dag |>
  tidy_dagitty() |>
  node_status()

colors <- met.brewer(name = "VanGogh1", n = 7, type = "discrete")
status_colors <- c(exposure = colors[3], outcome = colors[6], latent = "grey50")

# Fancy DAG
ggplot(ich_dag_tidy, aes(x = x, y = y, xend = xend, yend = yend)) +
  geom_dag_edges(aes(color = "grey50")) +
  geom_dag_point(aes(color = status), size = 20) +
  geom_dag_label_repel(aes(label = label, fill = status),
    seed = 1234,
    color = "white", fontface = "bold", family = "Cantarell", size = 5
  ) +
  scale_color_manual(values = status_colors, na.value = "grey20") +
  scale_fill_manual(values = status_colors, na.value = "grey20") +
  guides(color = FALSE, fill = FALSE)

ggdag_adjustment_set(ich_dag_tidy) +
  geom_dag_edges(aes(color = "grey50")) +
  geom_dag_point(aes(color = status), size = 20) +
  geom_dag_label_repel(aes(label = label, fill = status),
    seed = 1234,
    color = "white", fontface = "bold", family = "Cantarell", size = 5
  ) +
  scale_color_manual(values = status_colors, na.value = "grey20") +
  scale_fill_manual(values = status_colors, na.value = "grey20") +
  guides(color = FALSE, fill = FALSE)

ggdag_paths(ich_dag_tidy) +
  geom_dag_edges(aes(color = "grey50")) +
  geom_dag_point(aes(color = status), size = 20) +
  geom_dag_label_repel(aes(label = label, fill = status),
    seed = 1234,
    color = "white", fontface = "bold", family = "Cantarell", size = 5
  ) +
  scale_color_manual(values = status_colors, na.value = "grey20") +
  scale_fill_manual(values = status_colors, na.value = "grey20") +
  guides(color = FALSE, fill = FALSE)

adjustment_vars <- c("neurosurgery", "age", "ich_volume", "ivh", "gcs_baseline", "ich_location", "wlst")

control_for(ich_dag_tidy, var = adjustment_vars)

ggdag_adjust(ich_dag_tidy, var = adjustment_vars) +
  geom_dag_edges(aes(color = "grey50")) +
  geom_dag_point(aes(color = status), size = 20) +
  geom_dag_label_repel(aes(label = label, fill = status),
    seed = 1234,
    color = "white", fontface = "bold", family = "Cantarell", size = 5
  ) +
  scale_color_manual(values = status_colors, na.value = "grey20") +
  scale_fill_manual(values = status_colors, na.value = "grey20") +
  guides(color = FALSE, fill = FALSE)

ggdag_dseparated(ich_dag_tidy, controlling_for = adjustment_vars) +
  geom_dag_edges(aes(color = "grey50")) +
  geom_dag_point(aes(color = status), size = 20) +
  geom_dag_label_repel(aes(label = label, fill = status),
    seed = 1234,
    color = "white", fontface = "bold", family = "Cantarell", size = 5
  ) +
  scale_color_manual(values = status_colors, na.value = "grey20") +
  scale_fill_manual(values = status_colors, na.value = "grey20") +
  guides(color = FALSE, fill = FALSE)

@@

```{r}

### 2023-10-02 analysis/descriptive.qmd
ggdag updates

#
#
#
#
#

library(tidyverse)
library(dagitty)
library(ggdag)
library(MetBrewer)
library(here)
library(tableone)
library(gt)
library(gtExtras)
library(broom)

data <- read_csv(here("data", "all.csv"))

#
#
#
#
#
#| fig-width: 20

# have to fix time from symptom onset to presentation in ED (units seems to be jacked up)

table1_vars <- c("age", "sex", "race", "ethnicity", "htn", "dm2", "tobacco", "sbp_baseline", "gcs_baseline", "nihss_baseline", "ich_volume_baseline", "ivh", "ich_location", "neurosurgery_evac", "comfort_care_binary", "study")

table1 <- CreateTableOne(vars = table1_vars, data = data, strata = "ich_laterality")

table1

#
#
#

>>>>

---
title: "Descriptive Statistics"
code-fold: true
---

### 2023-10-02 analysis/models.qmd
ggdag updates

library(tidyverse)
library(dagitty)
library(ggdag)
library(MetBrewer)
library(here)
library(brms)
library(broom)
library(tableone)

@@

First let's do a Table 1

@@

CreateTableOne(data = data)

@@

>>>>

library(tidyverse)
library(marginaleffects)
library(brms)
library(ggplot2)
library(ggdist)
library(broom)
library(here)

@@

## Estimate the Causal Effect

First let's do a replication of the INTERACT re-analysis.

@@

priors <- c(prior(normal(0, 1.5), class = Intercept))

inits <- list(Intercept = c(-2, -1, 0, 1, 2, 2.5))

# mod <- brm(mrs_90 ~ 1,
#   data = data,
#   family = cumulative("logit"),
#   prior = priors,
#   init = rep(list(inits), 4),
#   chains = 4, iter = 5000 * 2, seed = 28203, cores = 4,
#   backend = "cmdstanr", refresh = 0
# )

@@

## Conduct Sensitivity Analyses
